Using an SMT engine to generate Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-03-11 2017-Xudong-SMT/ActaInformatica.tex

	\begin{tabular}{p{4cm}p{3cm}p{3cm}}
		\hline\specialrule{0em}{1pt}{1pt}
		Use-case & Brute force & Smart algorithm
                \\\specialrule{0em}{1pt}{1pt}
		\hline\specialrule{0em}{3pt}{3pt}
		Enable operator   			&
                5 SAT OTs           &
                5 SAT OTs
                \\\specialrule{0em}{1pt}{1pt}

                ``(P>Q)>R'' &
                55 UNSAT           &
                42 UNSAT
                \\\specialrule{0em}{1pt}{1pt}
		&
                376 ms 				&
                344 ms  
		\\\hline\specialrule{0em}{3pt}{3pt}
		SimpleProt    			&
                7 SAT OTs           &
                7 SAT OTs
                \\\specialrule{0em}{1pt}{1pt}

                (no holes)&
                260 UNSAT           &
                57 UNSAT
                \\\specialrule{0em}{1pt}{1pt}
		&
                1536 ms 				&
                359 ms  
%                \\\specialrule{0em}{1pt}{1pt}
%                \textsl{for any sort} & & $=,\ \ne$
		\\\hline\specialrule{0em}{1pt}{1pt}
		SimpleProt    			&
                19 SAT OTs           &
                19 SAT OTs
                \\\specialrule{0em}{1pt}{1pt}

                (with 2 client holes)&
                836 UNSAT           &
                185 UNSAT
                \\\specialrule{0em}{1pt}{1pt}
		&
                2496 ms 				&
                844 ms  
		\\\hline\specialrule{0em}{1pt}{1pt}
		FailureTimer    			&
                12 SAT OTs           &
                12 SAT OTs
                \\\specialrule{0em}{1pt}{1pt}

                (no Max Progress)&
                1253 UNSAT           &
                812 UNSAT
                \\\specialrule{0em}{1pt}{1pt}
		&
                1253 ms 				&
                812 ms

@@

>>>>

In each cell of the following table, we display the number of OTs whose predicates were founSAT/UNSAT by the SMT engine, and the overall time spent for the whole algorithm execution.

	\begin{tabular}{p{4cm}p{3cm}p{3cm}}
		\hline\specialrule{0em}{1pt}{1pt}
		Use-case & Brute force & Smart algorithm
                \\\specialrule{0em}{1pt}{1pt}
		\hline\specialrule{0em}{3pt}{3pt}
		Enable operator   			&
                5/55 OTs           &
                5/42 OTs
                \\\specialrule{0em}{1pt}{1pt}

                ``(P>Q)>R'' 		&
                376 ms 				&
                344 ms  
		\\\hline\specialrule{0em}{3pt}{3pt}
		SimpleProt    			&
                7/260 OTs           &
                7/57 OTs
                \\\specialrule{0em}{1pt}{1pt}

                (no holes)&
                1536 ms 				&
                359 ms  
%                \\\specialrule{0em}{1pt}{1pt}
%                \textsl{for any sort} & & $=,\ \ne$
		\\\hline\specialrule{0em}{1pt}{1pt}
		SimpleProt    			&
                19/836 OTs           &
                19/185 OTs
                \\\specialrule{0em}{1pt}{1pt}

                (with 2 client holes)&
                2496 ms 				&
                844 ms  
		\\\hline\specialrule{0em}{1pt}{1pt}
		FailureTimer    			&
                12/235 OTs           &
                12/180 OTs
                \\\specialrule{0em}{1pt}{1pt}

                (no Max Progress)&
                1253 UNSAT           &
                812 UNSAT
                \\\specialrule{0em}{1pt}{1pt}
		&
                1253 ms 				&
                812 ms  
		\\\hline\specialrule{0em}{1pt}{1pt}
		FailureTimer X 2    			&
                37/3136 OTs           &
                37/2416 OTs
                \\\specialrule{0em}{1pt}{1pt}

		&
                8923 ms 				&
                6798 ms

@@

        This shows a significant benefit of the ``smart'' strategy, in the considered use-cases, between 30 to 60\% gain depending on the examples.
